### 2012-06-14 inst/examples/Sethi_policyfns.Rmd
Sethi policy function (show libraries)

Clear the workspace and load package dependencies: 
``` {r  setup, echo=FALSE, cache=FALSE}
rm(list=ls())   
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
rm(list=ls())
````

>>>>

Clear the workspace and load package dependencies: 
``` {r  setup, cache=FALSE}
rm(list=ls())   
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
````
